---
title: "QMM Assignment"
author: "Sri Hari Vadhry"
date: "2023-09-23"
output: html_document
---

```{r}
library(lpSolve)
```

# Objective Function- How many products to be produced by each plant to maximize the profit and to check on avoiding layoff by using same percentage of excess production capacity

```{r}
objective <- c(420, 360, 300, 420, 360, 300, 420, 360, 300)

```

# Below are the constraints and Non negative constraints are assumed by default
1. Excess production capacity constraints
2. Storage capacity constraints
3. sales constraints
4. Employee layoff constraints

```{r}
constraints <- matrix(c(1, 1, 1, 0, 0, 0, 0, 0, 0,
                        0, 0, 0, 1, 1, 1, 0, 0, 0,
                        0, 0, 0, 0, 0, 0, 1, 1, 1,    
                        20, 15, 12, 0, 0, 0, 0, 0, 0,
                        0, 0, 0, 20, 15, 12, 0, 0, 0,
                        0, 0, 0, 0, 0, 0, 20, 15, 12,
                        1, 0, 0, 1, 0, 0, 1, 0, 0,
                        0, 1, 0, 0, 1, 0, 0, 1, 0,
                        0, 0, 1, 0, 0, 1, 0, 0, 1,
                        900, 900, 900, -750, -750, -750, 0, 0, 0,
                        0, 0, 0, 450, 450, 450, -900, -900, -900,
                        450, 450, 450, 0, 0, 0, -750, -750, -750), nrow=12, byrow= TRUE)
constraints
```

#Inequality Signs

```{r}
signs <-c("<=",
          "<=",
          "<=",
          "<=",
          "<=",
          "<=",
          "<=",
          "<=",
          "<=",
          "=",
          "=",
          "=")
```

# Right Hand Side Coefficents̥

```{r}
rhs <- c(750,
         900,
         450,
         13000,
         12000,
         5000,
         900,
         1200,
         750,
         0,
         0,
         0)
```

# Profit maximization
```{r}

Maximize_Z = lp("max", objective, constraints, signs, rhs, int.vec = 1:9)

Maximize_Z
```

# Decision Variables

```{r}
Maximize_Z$solution

```


